E-Graphs With Bindings

### 2025-01-19 LICS_2025/e_graphs_with_bindings/sections/categorical_semantics.tex
wip

A set of $\Sigma$-terms generated by monoidal signature $\Sigma$ is given by the following grammar
\[
\tau \Coloneq \phi \;|\; \id_{I} \;|\; \id_{A} \;|\; \sym_{A,B} \;|\; \tau_{1};\tau_{2} \;|\; \tau_{1} \otimes \tau_{2}
\],
where $\phi$ ranges over the set of generators $\Sigma_{M}$ and $A,B$ range over the set of objects $\Sigma_{O}$.
\end{definition}

@@

\begin{definition}
\label{def:closed}
A monoidal (right) closed category is a monoidal category $\catname{C}$ satisfying for
every pair of objects $B,C$ there is an object $B \xRightarrow{} C$ and a morphism $\textbf{ev}_{B,C} : (B \xRightarrow{} C) \otimes B \to
C$, and for every triple of objects $A,B,C$ there is an operation $\Lambda_{A,B,C} : \catname{C}(A \otimes B,C) \to
\catname{C}(A,B \xRightarrow{} C)$ satisfying the following equations for all $f : A \otimes B \to C$ and $g : Z \to A$:
\begin{itemize}
\item $f = \Lambda_{A,B,C}(f) \otimes \id_{B}; \textbf{ev}_{B,C}$
\item $\id_{B \xRightarrow{} C} = \Lambda_{B \xRightarrow{} C,B,C}(\textbf{ev}_{B,C})$
\item $\Lambda_{Z,B,C}(g \otimes \id_{B}; f) = g;\Lambda_{A,B,C}(f)$
\end{itemize}
\end{definition}

This definition is equivalent to the more usual one that defines a (right) closed category through a pair of adjoint functors $- \otimes B$ and $B \xRightarrow{} -$~\cite{ghica-zanassi2023string}.
If the tensor is symmetric, then the category is simply \textit{closed}.

@@

\textit{Closed} $\Sigma$-terms are given by the following grammar
\[
    \tau \coloneq \phi \;|\; \id_{I} \;|\; \id_{A} \;|\; \sym_{A,B} \;|\; \tau_{1};\tau_{2} \;|\; \tau_{1} \otimes \tau_{2} \; | \; \textbf{ev}_{A,B} \; | \; \Lambda(\tau)
\]
, where the types are given as
\[
A,B \coloneq T \;|\; A \otimes B \; | \; A \xRightarrow{} B
\], where $T$ is in $\Sigma_{O}$.
\end{definition}

\begin{definition}
The free closed symmetric monoidal category $\catname{Sc}(\Sigma)$ is given by a set of closed $\Sigma$-terms quotiented by the laws of a symmetric monoidal category and the equations from Definition~\ref{def:closed}.
\end{definition}

To encode equivalences between morphisms (or $\Sigma$-terms), the hom-sets of the corresponding free categories can be endowed with additional structure of a semilattice induced by an idempotent, commutative and associative operator $+$.
This endowment turns such categories into $\catname{SLat}$-enriched categories where $\catname{SLat}$ is a category of \textit{unbounded} semilattices and homomorphisms between them.

\begin{definition}[Semilattice-enriched category]
    A semilattice-enriched category $\mathbb{C}$ is defined by the following data
    \begin{itemize}
        \item a set of objects $\mathbb{C}$
        \item for every pair of objects $A,B \in \mathbb{C})$ --- a hom-object $\mathbb{C}(A,B \in \catname{SLatt}$
        \item for every triple of objects $A,B,C \in \mathbb{C}$ --- a composition morphism
        \[
            \circ: \mathbb{C}(B,C) \otimes \mathbb{C}(A,B) \to \mathbb{C}(A,C)
        \]
        \item for every object $A \in C$ --- a unit morphism
        \[
        u_{A} : I \to \mathbb{C}(A,A), \text{ where $I$ is the monoidal unit for $\catname{SLatt}$}
        \]
    \end{itemize}
    such that particular coherence diagrams commute~\cite{Borceux_1994}.
\end{definition}

\begin{definition}[Semilattice-enriched SMC]\label{def:enriched-prop}
    A \textit{semilattice enriched strict SMC}  $\mathbb{C}$ is given by a semilattice-enriched category $\mathbb{C}$ as above that additionally has
    \begin{itemize}
    \item a unit object $I_{C} \in \mathbb{C}$
    \item for every pair of objects $A,B \in \mathbb{C}$ --- an object $A \otimes B \in \mathbb{C}$
    \item for all $A,B,C,D$ --- a tensor morphism $ - \otimes_{C} - : \mathbb{C}(A,C) \otimes \mathbb{C}(B,D) \to \mathbb{C}(A \otimes B, C \otimes D)$
    \end{itemize}
    such that particular coherence diagrams commute~\cite{enriched_monoidal}.
    \end{definition}
    The latter morphism being in $\catname{SLatt}$ implies the following equations that $\otimes$ satisfy
    \[
    f \otimes (g+h) = f \otimes g + f \otimes h \qquad (f+g) \otimes h = f \otimes h + g \otimes h
    \]

@@

    \begin{proposition}(A specialized case of Proposition 6.4.7~\cite{Borceux_1994})
    There is a 2-adjunction 
    % https://q.uiver.app/#q=WzAsMixbMCwwLCJcXGNhdG5hbWV7U0xhdHR9LVxcY2F0bmFtZXtDYXR9Il0sWzIsMCwiXFxjYXRuYW1le0NhdH0iXSxbMSwwLCJGIiwyLHsiY3VydmUiOjR9XSxbMCwxLCJHIiwyLHsiY3VydmUiOjR9XSxbMiwzLCIiLDAseyJsZXZlbCI6MSwic3R5bGUiOnsibmFtZSI6ImFkanVuY3Rpb24ifX1dXQ==
    \[\begin{tikzcd}
        \catname{SLatt}\text{--}\catname{Cat}\arrow[rr, "\mathcal{U}", bend left] & \hspace{-1em}\top & \catname{Cat} \arrow[ll, "\mathcal{F}", bend left]
        \end{tikzcd}
    \]
    that is induced by a usual free-forgetful adjunction

    \[\begin{tikzcd}
        \catname{SLatt} \arrow[rr, "U", bend left] & \top & \catname{Set} \arrow[ll, "F", bend left]
        \end{tikzcd}
    \]
    \end{proposition}

In particular, 2-functor $\mathcal{F}$ turns every category $\mathbb{C'} \in \catname{Cat}$ into a free semilattice enriched $\mathbb{C} \in \catname{SLat}\text{--}\catname{Cat}$ by making every hom-set of $\mathbb{C'}$ into a free semilattice on this set.
Being a 2-functor it also lifts an adjunction in $\catname{Cat}$ $F \dashv G$ into an $\catname{Slat}$-adjunction.
Thus, applying the functor to $\catname{Sc}(\Sigma)$ we get a closed symmetric monoidal $\catname{Slat}$-category $\catname{Sc}(\Sigma)^{+}$ by lifting the adjunction $- \otimes B \dashv B \xRightarrow{} -$.

>>>>

A set of $\Sigma$-terms generated by monoidal signature $\Sigma$ is given by the following grammar
\[
\tau \coloneqq \phi \;|\; \id_{I} \;|\; \id_{A} \;|\; \sym_{A,B} \;|\; \tau_{1};\tau_{2} \;|\; \tau_{1} \otimes \tau_{2}
\],
where $\phi$ ranges over the set of generators $\Sigma_{M}$ and $A,B$ range over the set of objects $\Sigma_{O}$.
\end{definition}

@@

\begin{definition}
\label{def:closed}
A monoidal (right) closed category is a monoidal category $\catname{C}$ satisfying for
every pair of objects $B,C$ there is an object $B \multimap C$ and a morphism $\textbf{ev}_{B,C} : (B \multimap C) \otimes B \to
C$, and for every triple of objects $A,B,C$ there is an operation $\Lambda_{A,B,C} : \catname{C}(A \otimes B,C) \to
\catname{C}(A,B \multimap{} C)$ satisfying the following equations for all $f : A \otimes B \to C$ and $g : Z \to A$:
\begin{itemize}
\item $f = \Lambda_{A,B,C}(f) \otimes \id_{B}; \textbf{ev}_{B,C}$
\item $\id_{B \multimap{} C} = \Lambda_{B \multimap{} C,B,C}(\textbf{ev}_{B,C})$
\item $\Lambda_{Z,B,C}(g \otimes \id_{B}; f) = g;\Lambda_{A,B,C}(f)$
\end{itemize}
\end{definition}

This definition is equivalent to the more usual one that defines a (right) closed category through a pair of adjoint functors $- \otimes B$ and $B \multimap{} -$~\cite{ghica-zanassi2023string}.
If the tensor is symmetric, then the category is simply \textit{closed}.

@@

\textit{Closed} $\Sigma$-terms are defined inductively by first defining a family of objects $obj_{\Sigma_{O}}$.
\begin{itemize}
\item A designated $I$ is in $obj_{\Sigma_{O}}$.
\item If $A \in obj_{\Sigma_{O}}$ and $B \in obj_{\Sigma_{O}}$, then $A \otimes B \in obj_{\Sigma_{O}}$ and $A \multimap B \in obj_{\Sigma_{O}}$.
\end{itemize}
A family of closed $\Sigma$ terms is then defined as
\begin{itemize}
    \item $\phi : A \to B \in \Sigma_{M}$ is a closed $\Sigma$-term.
    \item If $A$ and $B$ are $obj_{\Sigma_{O}}$, then $\id_{A}$ and $\sym_{A,B}$ are closed $\Sigma$-terms.
    \item If $f : A \to B$ and $g : B \to C$ are closed $\Sigma$-terms, then so is $f;g : A \to C$. 
    \item If $f : A \to B$ and $g : C \to D$ are closed $\Sigma$-terms, then so is $f \otimes g : A \otimes C \to B \otimes D$.
    \item If $A$ and $B$ are $obj_{\Sigma_{O}}$, then $\textbf{ev}_{A,B} : A \multimap B \otimes A \to B$ is a closed $\Sigma$-term.
    \item If $h : X \otimes A \to B$ is a closed $\Sigma$-term, then $\Lambda_{X,A,B}(h) : X \to (A \multimap B)$ is a closed $\Sigma$-term.
\end{itemize}
\end{definition}

\begin{definition}
The free closed symmetric monoidal category $\catname{CS}(\Sigma)$ is given by a set of closed $\Sigma$-terms quotiented by the laws of a symmetric monoidal category and the equations from Definition~\ref{def:closed}.
\end{definition}

To encode equivalences between morphisms (or $\Sigma$-terms), the hom-sets of the corresponding free categories can be endowed with additional structure of a semilattice induced by an idempotent, commutative and associative operator $+$.
This endowment turns such categories into $\catname{SLat}$-enriched categories where $\catname{SLat}$ is a category of \textit{unbounded} semilattices and homomorphisms between them (see Appendix section~\ref{sec:appendix:1}).

\begin{definition}[Semilattice-enriched category]
    A semilattice-enriched category $\mathbb{C}$ is defined by the following data
    \begin{itemize}
        \item a set of objects $\mathbb{C}$
        \item for every pair of objects $A,B \in \mathbb{C}$ --- a hom-object (or, hom-semilattice) $\mathbb{C}(A,B) \in \catname{SLat}$
        \item for every triple of objects $A,B,C \in \mathbb{C}$ --- a composition morphism
        \[
            \circ: \mathbb{C}(B,C) \otimes \mathbb{C}(A,B) \to \mathbb{C}(A,C)
        \]
        \item for every object $A \in C$ --- a unit morphism
        \[
        u_{A} : I \to \mathbb{C}(A,A), \text{ where $I$ is the monoidal unit for $\catname{SLat}$}
        \]
    \end{itemize}
    such that particular coherence diagrams commute~\cite{Borceux_1994}.
\end{definition}

\begin{definition}[$\catname{SLat}$-functor]
	Let $\mathbb{C}$ and $\mathbb{D}$ be two $\catname{SLat}$-categories.
	An $\catname{SLat}$-functor $F : \mathbb{C} \to \mathbb{D}$ is defined by the following data.
	\begin{itemize}
	  \item A mapping $F : \mathbb{C} \to \mathbb{D}$
	  \item An object-indexed family of morphisms in $\catname{SLat}$ $F_{A,B} : \mathbb{C}(A,B) \to \mathbb{D}(FA,FB)$
	\end{itemize}
	such that certain coherence diagrams commute~\cite{Borceux_1994}.
	$F$ being a morphism in $\catname{SLat}$ has a property $F(f + g) = F(f) + F(g)$.
\end{definition}

\begin{definition}[Semilattice-enriched SMC]\label{def:enriched-prop}
    A \textit{semilattice enriched strict SMC}  $\mathbb{C}$ is given by a semilattice-enriched category $\mathbb{C}$ as above that additionally has
    \begin{itemize}
    \item a unit object $I_{C} \in \mathbb{C}$
    \item for every pair of objects $A,B \in \mathbb{C}$ --- an object $A \otimes B \in \mathbb{C}$
    \item for all $A,B,C,D$ --- a tensor morphism $ - \otimes_{C} - : \mathbb{C}(A,C) \otimes \mathbb{C}(B,D) \to \mathbb{C}(A \otimes B, C \otimes D)$
    \end{itemize}
    such that particular coherence diagrams commute~\cite{enriched_monoidal}.
    \end{definition}
    The latter morphism being in $\catname{SLat}$ implies the following equations that $\otimes$ satisfy
    \[
    f \otimes (g+h) = f \otimes g + f \otimes h \qquad (f+g) \otimes h = f \otimes h + g \otimes h
    \]

@@

    \begin{proposition}(A specialized case of Proposition 6.4.7~\cite{Borceux_1994})
    There is a 2-adjunction 
    % https://q.uiver.app/#q=WzAsMixbMCwwLCJcXGNhdG5hbWV7U0xhdHR9LVxcY2F0bmFtZXtDYXR9Il0sWzIsMCwiXFxjYXRuYW1le0NhdH0iXSxbMSwwLCJGIiwyLHsiY3VydmUiOjR9XSxbMCwxLCJHIiwyLHsiY3VydmUiOjR9XSxbMiwzLCIiLDAseyJsZXZlbCI6MSwic3R5bGUiOnsibmFtZSI6ImFkanVuY3Rpb24ifX1dXQ==
    \[\begin{tikzcd}
        \catname{SLat}\text{--}\catname{Cat}\arrow[rr, "\mathcal{U}", bend left] & \hspace{-1em}\top & \catname{Cat} \arrow[ll, "\mathcal{F}", bend left]
        \end{tikzcd}
    \]
    that is induced by a usual free-forgetful adjunction

    \[\begin{tikzcd}
        \catname{SLat} \arrow[rr, "U", bend left] & \top & \catname{Set} \arrow[ll, "F", bend left]
        \end{tikzcd}
    \]
    \end{proposition}

In particular, 2-functor $\mathcal{F}$ turns every category $\mathbb{C'} \in \catname{Cat}$ into a free semilattice enriched $\mathbb{C} \in \catname{SLat}\text{--}\catname{Cat}$ by making every hom-set of $\mathbb{C'}$ into a free semilattice on this set.
Being a 2-functor it also lifts an adjunction in $\catname{Cat}$ $F \dashv G$ into an $\catname{Slat}$-adjunction.
Thus, applying the functor to $\catname{CS}(\Sigma)$ we get a closed symmetric monoidal $\catname{Slat}$-category $\catname{CS}(\Sigma)^{+}$ by lifting the adjunction $(- \otimes B, B \multimap{} -, \eta, \varepsilon)$.
We can similarly derive $\catname{SLat}$-enriched versions of  $\Lambda_{A,B,C}$ and $\textbf{ev}_{A,B}$ morphisms using the lifted adjunction as $\textbf{ev}_{A,B} = \varepsilon_{A}$ and $\Lambda_{A,B,C}(f) = \eta; (B \multimap{} f)$.
The following equation can then be derived which will be useful in encoding equivalences inside abstractions.
\begin{align*}
\Lambda_{A,B,C}(f + g) &= \eta;(B \multimap (f + g))\\
                       &= \eta;(B \multimap (f) + B \multimap (g))\\
                       &= \eta;(B \multimap (f)) + \eta;(B \multimap (g))\\
                       &= \Lambda_{A,B,C}(f) + \Lambda_{A,B,C}(g)
\end{align*}

Similar to $\catname{CS}(\Sigma)$, $\catname{CS}(\Sigma)^{+}$ can be freely generated from a set of $\Sigma^{+}$-terms.

### 2025-01-19 LICS_2025/e_graphs_with_bindings/sections/combinatorial_semantics.tex
wip

@@

\begin{definition}
Closed monoidal signature $\Sigma$ is a pair $(\Sigma_{O},\Sigma_{M})$ of signatures for objects and signatures for morphisms with sources and targets in $\text{obj}_{\Sigma_{O}}$ defined as
\begin{itemize}
  \item $I$ (monoidal unit) is in $\text{obj}_{\Sigma_{O}}$
  \item For every $o \in \Sigma_{O}$, $o \in \text{obj}_{\Sigma_{O}}$;
  \item For every $o_1$ and $o_2$ $ \in \text{obj}_{\Sigma_{O}}$, $o_1 \otimes o_2 \in \text{obj}{\Sigma_{O}}$ and $o_1 \multimap o_2 \in \text{obj}_{\Sigma_{O}}$
\end{itemize}
\end{definition}

\begin{definition}
 Closed symmetric monoidal theory ($\catname{CSMT}$) over a closed monoidal signature $\Sigma$ and equations $\mathcal{E}$ denoted as $\catname{CSMT}(\Sigma, \mathcal{E})$ is given by a set of terms $T$
 \begin{align*}
 T \coloneq\; &t : A \to B \in \Sigma_{M} \;|\; t_1 \otimes t_2 : A \otimes C \to B \otimes D \text{ for } t_{1} : A \to B, t_{2} : C \to D \in T\\
            & \;|\; t_{1};t_{2} : A \to C \text{ for } t_{1} : A \to B, t_{2} : B \to C \in T \; | \;  \Lambda(t) : A \to X \multimap B \text{ for } t : A \otimes X \to B \\
            &  \;|\; \text{eval}(t_1 \otimes t_2) : B \text{ for } t_1 : X \multimap B, t_2 : X \in T \\
            &  \;|\; \text{sym}_{A,B} \;|\; id_{A}
 \end{align*}
 quotiented by the laws of a closed symmetric monoidal category.
\end{definition}
% \question{Maybe types and terms combined is not a good idea}
\begin{definition}

We define an e-hypergraph $\mathcal{G}$ over a closed symmetric monoidal signature $\Sigma$ as a tuple $(V,E,s,t, l_{V}, l_{E} \textcolor{red}{<}, \textcolor{blue}{<},\consistency)$ where
\begin{itemize}
  \item $V$ is a set of vertices;
  \item $E = \textcolor{gray}{E} \cup \textcolor{red}{E} \cup \textcolor{blue}{E}$ is a set of hyperedges that include \textit{plain} edges and two types of \textit{hierarchical} edges respectively;
  \item $s,t : E \to V^{*}$ are source and target functions;
  \item $l_{E} : E \to \Sigma_{M} + 1$, $l_{V} : V \to \text{obj}_{\Sigma_{O}}$ are \textit{label} functions;
  \item $\textcolor{red}{<} : V + E \to \textcolor{red}{E}$ and $\textcolor{blue}{<} : V + E \to \textcolor{blue}{E}$ are partial \textit{child} functions that are disjoint: if $\textcolor{red}{<}(x)$ is defined then $\textcolor{blue}{<}(x)$ is undefined and vice-versa;
  \item $\consistency = \bigcup_{p} \consistency_{p}$, where $\consistency_{p}$ is a \textit{consistency} relation defined on each set $\{x \in V + E \;|\; p \;\textcolor{red}{<^{\mu}}\; x\}$;
\end{itemize} 
\end{definition}

$\textcolor{red}{E}$ will contain edges that encode the equivalence classes and $\textcolor{blue}{E}$ the ones that defined the lambda abstraction.
All the above functions and relations must satisfy the obvious properties (TODO: add them).

@@

Consider an example of isomorphic and non-isomorphic cospans below and their respective string diagrams

\begin{figure}
  \begin{subfigure}[c]{0.4\linewidth}
    \[
    \adjustbox{scale=0.6}{
    \tikzfig{./figures/closed_iso_example_1}
    }
    \]
  \end{subfigure}
  \hfill
  \begin{subfigure}[c]{0.4\linewidth}
    \[
    \adjustbox{scale=0.6}{
    \tikzfig{./figures/closed_iso_example_2}
    }
    \]
  \end{subfigure}
\end{figure}

@@

>>>>

\textcolor{red}{Add intro to hypergraphs}

@@

\begin{definition}
We define an e-hypergraph $\mathcal{G}$ over a closed symmetric monoidal signature $\Sigma = (\Sigma_{O}, \Sigma_{M})$ as a tuple $(V,E,s,t, l_{V}, l_{E} \textcolor{red}{<}, \textcolor{blue}{<},\consistency)$ where
\begin{itemize}
  \item $V$ is a set of vertices.
  \item $E = \textcolor{gray}{E} \cup \textcolor{red}{E} \cup \textcolor{blue}{E}$ is a set of hyperedges that that is formed of three disjoint sets of hyperedges defined below.
  \item $s,t : E \to V^{*}$ are source and target functions.
  \item $l_{E} : E \to \Sigma_{M} + 1$, $l_{V} : V \to \Sigma_{O} \cup \text{obj}_{\multimap}$ are \textit{label} functions, where $\text{obj}_{\multimap}$ consists of objects $A \multimap B$ for $A,B \in obj_{\Sigma_{O}}$.
  \item $\textcolor{red}{<} \subseteq \textcolor{red}{E} \times V + E$ and $\textcolor{blue}{<} \subseteq \textcolor{blue}{E} \times V + E $ with $\textcolor{red}{E}, \textcolor{blue} \subset E$ are disjoint partial orders.
        For $x \in V + E$, the set of predecessors of $x$ is denoted as $[x) = \{x' ~|~ \exists y_{1} = x', \ldots, y_{n} = x,  y_{i} \textcolor{red}{<^{\mu}} y_{i + 1} \text{ or } y_{i} \textcolor{blue}{<^{\mu}} y_{i+1}\; \}$.
        We will denote the immediate predecessor $y$ of $x$ as $y \textcolor{red}{<^{\mu}} x$ and $y \textcolor{blue}{<^{\mu}} x$.
        We will call edges $e$ such that $l(e) = \bot$ hierarchical and edges $e$ and vertices $v$ such that $[e) = \varnothing$ and $[v) = \varnothing$ \textit{top-level}.
        Each of these relations should satisfy the following
        \begin{enumerate}
          \item each set of predecessors consists exclusively of hierarchical edges;
          \item each $x$ has at most one immediate predecessor;
          \item edges $e$ such that there is no $x$ such that $e \textcolor{red}{<^{\mu}} x$ or $e \textcolor{red}{<^{\mu}} x$ are labelled;
          \item the relations are closed under connectivity, \emph{i.e.}, if $v \in s(e)$ then $e' \textcolor{red}{<^{\mu}} e$ iff $e' \textcolor{red}{<^{\mu}} v$, similarly for $v \in t(e)$ and $\textcolor{blue}{<}$.
        \end{enumerate}
  \item $\consistency$ is a \textit{consistency relation} which is given by the union of a family of equivalence relations $\consistency_p$ on each set $\{x \in V + E ~|~ p \textcolor{red}{<^\mu} x\}$ of elements which share the same parent where each relation is also closed under connectivity, \textit{i.e.}, if $v \in s(e)$ or $v \in t(e)$ such that $p \textcolor{red}{<^{\mu}}(v)$ and $p \textcolor{red}{<^{\mu}}(e)$ then $v \consistency_{p} e$.
  We require that $\consistency_{p} \not = (E_{p} + V_{p}) \times (E_{p} + V_{p})$ where $V_{p} = \{ v ~ | ~ p \textcolor{red}{<^{\mu}} v\}$ and $E_{p} = \{ e ~ | ~ p \textcolor{red}{<^{\mu}} e\}$.
\end{itemize} 
$\textcolor{red}{E}$ and $\textcolor{blue}{E}$ are then induced by the corresponding relations can consist of exclusively hierarchical edges, then we have $\textcolor{gray}{E} = E \setminus \textcolor{red}{E} \cup \textcolor{blue}{E}$.
\end{definition}

Intuitively, edges from $\textcolor{red}{E}$ will encode equivalence classes, \emph{i.e.}, e-boxes, while edges from $\textcolor{blue}{E}$ will encode lambda-abstraction boxes.

Consider an example in the middle part of Figure~\ref{fig:e-cospan-example}.
The e-hypergraph in the example is given by $V = \{v_{1}, \ldots w_{10}\}$, $E = \{e_{1}, \ldots, e_{7}\}$, $l_{E} = {e_{1} \mapsto \bot, e_{2} \mapsto \bot, e_{3} \mapsto g, \ldots, e_{7} \mapsto f}$ and then we have
\[
\begin{array}{cccc}
  v_{4} \textcolor{red}{<^{\mu}} e_{1} & v_{7} \textcolor{blue}{<^{\mu}} e_{2} & v_{4} \consistency e_{3} & v_{4} \not \consistency v_{10}\\
  e_{3} \textcolor{red}{<^{\mu}} e_{1} & e_{5} \textcolor{blue}{<^{\mu}} e_{2} &  e_{3} \consistency u_{1} & e_{2} \not \consistency e_{6}\\
  e_{2} \textcolor{red}{<^{\mu}} e_{1} & w_{7} \textcolor{blue}{<^{\mu}} e_{2} & e_{2} \consistency e_{4} & e_{4} \not \consistency e_{7}\\  
  \ldots & \ldots & \ldots & \ldots \\
  v_{12} \textcolor{red}{<^{\mu}} e_{1} & w_{9} \textcolor{blue}{<^{\mu}} e_{2} & v_{11} \consistency v_{12} & w_{6} \not \consistency w_{10}
\end{array}
\]
$\consistency_{e_{1}}$ defines a partition on immediate successors of $e_{1}$ which we delimit by a vertical dashed line.
Edges in $\textcolor{red}{E}$ are depicted with a dashed box, while edges in $\textcolor{blue}{E}$ --- with a round solid box.

\begin{figure}

\[
\adjustbox{scale=0.6}{
\tikzfig{./figures/closed_iso_example_2}
}
\]
\caption{Cospan of e-hypergraphs example}
\label{fig:e-cospan-example}
\end{figure}

\begin{definition}[E-hypergraph homomorphism]
TODO
\end{definition}

E-hypergraphs and their homomorphisms define a category $\catname{EHyp}({\Sigma})$.

@@

% Consider an example of isomorphic and non-isomorphic cospans below and their respective string diagrams

% \begin{figure}
%   \begin{subfigure}[c]{0.4\linewidth}
%     \[
%     \adjustbox{scale=0.6}{
%     \tikzfig{./figures/closed_iso_example_1}
%     }
%     \]
%   \end{subfigure}
%   \hfill
%   \begin{subfigure}[c]{0.4\linewidth}
%     \[
%     \adjustbox{scale=0.6}{
%     \tikzfig{./figures/closed_iso_example_2}
%     }
%     \]
%   \end{subfigure}
% \end{figure}

@@

\textcolor{red}{TODO: dpo rewriting}
